---
title: "R Notebook"
output: html_notebook
---

# Package Name

```{r}
available::available("nomisr")
```

# Good practice

```{r}
goodpractice::gp()
```

Everything is good! 
Well done ! There was still medium coverage at the submission, it is 100% now. 

> Verify Test on travis.

# Fonction / Variable Naming

# Readme

```
* The package name
* Badges for continuous integration and test coverage, the badge for rOpenSci peer-review once it has started (see below), and any other badges
* Short description of the package
* Installation instructions
* Brief demonstration usage
* If applicable, how the package compares to other similar packages and/or how it relates to other packages
* Citation information
```

+ I would be more precise on what the NOMIS database is. Submission issue mentionned UK database but not the README. While reviewing, I had a doubt and went to check on [NOMIS](https://www.nomisweb.co.uk/).
+ More documentation needed on the functions and the examples
+ Put package documentation link in the title of the repo like in the [`reprex`](https://github.com/tidyverse/reprex). By the way, you can add a more descriptive description on your github repo and some tags. 
+  could precise that it uses the tibble format (from the tidyverse)

# About the API

I went to the documentation and saw SMDX. Know that there is package for that. 

# Vignette

+ There is a vignette for introduction. 
+ About the format, it is `html_document` not `html_vignette`. May not be important
+ not build - **to check**

# Examples

+ All the example have a don't run statement. Check for other API package and on the book

# DESCRIPTION 

+ no need to *Author* field if using *Authors@R*

# Various

+ [minor] I would put the url of the API in its own variable. I think it is better practice and more efficient to maintain in case of change in the url (e.g *V0.2*). The url is used several time and a change would mean copy pasting. another utils function could help building the url (`paste0` is used three times)
+ `suppressMessage` is used to not show the message of `readr::read_csv`. However, the message appears because column are guessed and not set. It is good practice to set column type in `readr`. In an API package like this one, it make even more sense because it could helps be aware of any change in the format. 

# Functionnality

+ 

