---
title: "R Notebook"
output: html_notebook
---

# Package Name

```{r}
available::available("nomisr")
```

# Good practice

```{r}
goodpractice::gp()
```

Everything is good! 
Well done ! There was still medium coverage at the submission, it is 100% now. 

# Fonction / Variable Naming

# Readme

```
* The package name
* Badges for continuous integration and test coverage, the badge for rOpenSci peer-review once it has started (see below), and any other badges
* Short description of the package
* Installation instructions
* Brief demonstration usage
* If applicable, how the package compares to other similar packages and/or how it relates to other packages
* Citation information
```

+ I would be more precise on what the NOMIS database is. Submission issue mentionned UK database but not the README. While reviewing, I had a doubt and went to check on [NOMIS](https://www.nomisweb.co.uk/).
+ More documentation needed on the functions and the examples
+ Put package documentation link in the title of the repo like in the [`reprex`](https://github.com/tidyverse/reprex). By the way, you can add a more descriptive description on your github repo and some tags. 


# About the API

I went to the documentation and saw SMDX. Know that there is package for that. 

